### 2018-04-20 Manuscripts/model-descriptions/packer/gamma_invariance.tex
Trying out another version of PACKER, where this time tradeoff is implemented as weights for both contrast and target similarities.

\begin{equation} a(y_i, x) = \sum_j{f(x_j) s(y_i, x_j)}
\label{eq:aggsim}
\end{equation} where $f(x_j) = \gamma$ when $x_j$ is a member of a target category and $f(x_j) =
\gamma - 1$ when $x_j$ is a member of a contrast category.

@@

\begin{equation} a(y_i,x) = \gamma \sum_k{s(y_i,x_k)} + (\gamma-1) \sum_l{s(y_i,x_l)}
\label{eq:aggsimsplit}
\end{equation} where $k$ iterates over members of the target category and $l$ iterates over members
of the contrast category. To make the algebra a little less tedious we can simplify some of the
representations here. Let $t_i = \sum_k{s(y_i,x_k)}$ and $c_i = \sum_l{s(y_i,x_l)}$, which allows us to
express Equation \ref{eq:aggsimsplit} as:

@@

According to the implementation of PACKER as seen in the manuscript, an exponentiated Luce's choice
rule is used to find the probability $p$ of generating candidate $y_i$:

\begin{equation} p(y_i) = \dfrac{\exp \{\theta \cdot a(y_i, x)\}} {\sum_i{\exp \{\theta \cdot
a(y_i,x)\}}} .
\end{equation} 
Thus far, these equations only apply to predictions of category generation. However, predictions of
category assignments require some reconceptualization of these equations, although most of the
equations retain the same structure. Specifically, for Equations \ref{eq:aggsim} to
\ref{eq:aggsimsimp}, $y_i$ now represents the assignment of candidate $y$ to target category $i$.

expanding $a(y_i,x)$ with Equation \ref{eq:aggsimsimp}:
\begin{equation} p(y_i) = \dfrac{\exp \{\theta \cdot \gamma t_i + (\gamma-1) c_i\}} {\sum_i {\exp
      \{\theta \cdot \gamma t_i + (\gamma-1) c_i\}}}
\label{eq:expluceexp}
\end{equation}

>>>>

\begin{equation} a(y_i, x) = \sum_j{f(x_j) s(y_i, x_j)}
\label{eq:aggsim}
\end{equation} where $f(x_j) = \gamma$ when $x_j$ is a member of a target
category $T$ and $f(x_j) = \gamma - 1$ when $x_j$ is a member of a contrast
category $C$.

@@

\begin{equation} a(y_i,x) = \gamma \sum_{k \in K_T}{s(y_i,x_k)} + (\gamma-1)
\sum_{k \in K_C}{s(y_i,x_k)}
\label{eq:aggsimsplit}
\end{equation} where $K_T$ is the set of all target category members and $K_C$ is
the set of all members of the contrast category. To make the algebra a little
less tedious we can simplify some of the representations here. Let $t_i =
\sum_{k \in K_T}{s(y_i,x_k)}$ and $c_i = \sum_{k \in K_C}{s(y_i,x_k)}$, which allows
us to express Equation \ref{eq:aggsimsplit} as:

@@

According to the implementation of PACKER in the manuscript, an exponentiated
Luce's choice rule is used to find the probability $p$ of generating candidate
$y_i$:

\begin{equation} p(y_i) = \dfrac{\exp \{\theta \cdot a(y_i, x)\}} {\sum_i{\exp
\{\theta \cdot a(y_i,x)\}}} .
\label{expluce}
\end{equation} Thus far, Equation \ref{expluce} only apply to predictions of
category generation. In order to extend PACKER to category assignment
predictions, we need to find not the probability of generating candidate $y_i$,
but rather, the probability of assigning candidate $y_i$ to the target category. 
 these equations only apply to predictions of category
generation. However, predictions of category assignments require some
reconceptualization of these equations, although most of the equations retain
the same structure. Specifically, for Equations \ref{eq:aggsim} to
\ref{eq:expluce}, $i$ now iterates over each category (as opposed to each
generation candidate; i.e., $i \in K$ $ y_i$ now represents the assignment of candidate $y$ to
target category $i$.

Substituting $a(y_i,x)$ with Equation \ref{eq:aggsimsimp}:
\begin{equation} p(y_i) = \dfrac{\exp \{\theta \cdot \gamma t_i + (\gamma-1)
c_i\}} {\sum_i {\exp \{\theta \cdot \gamma t_i + (\gamma-1) c_i\}}}
\label{eq:expluceexp}
\end{equation}
